\documentclass[12pt,english]{article}
\usepackage[a4paper,bindingoffset=0.2in,%T
            left=1in,right=1in,top=1in,bottom=1in,%
            footskip=.25in]{geometry}
\usepackage{blindtext}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{titling}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{listings}
\usepackage{lettrine} 
\usepackage{tikz}  
\usepackage{color}
\setlength{\parskip}{12pt}
\begin{document}
\newgeometry{left=0.8in,right=0.8in,top=1in,bottom=1in}
\begin{center}
    \Large
    \textbf{Homework 4}\\
    \small
    \today\\
    \large
    Jose Carlos Munoz
\end{center}
%===============================
\section*{1}
\begin{align*}
C_a &= \frac{2 * d_a}{m_a * (m_a -1)} &= \frac{2 *3}{4 * (4-1)} &= \frac{1}{2}\\
C_b &= \frac{2 * d_b}{m_b * (m_b -1)} &= \frac{2 *1}{2 * (2-1)} &= 1\\
C_c &= \frac{2 * d_c}{m_c * (m_c -1)} &= \frac{2 *3}{4 * (4-1)} &=  \frac{1}{2}\\
C_d &= \frac{2 * d_d}{m_d * (m_d -1)} &= \frac{2 *1}{2 * (2-1)} &= 1\\
C_e &= \frac{2 * d_e}{m_e * (m_e -1)} &= \frac{2 *5}{4 * (4-1)} &=  \frac{5}{6}\\
C_f &= \frac{2 * d_f}{m_f * (m_f -1)} &= \frac{2 *1}{2 * (2-1)} &= 1\\
\end{align*}
\section*{2}
The Mypic path is from node n to k to j to e to f. The shortest path is from n to m to l to f
\section*{3}
We expect that D would be a higher than C. This is because the "Close-friend" List. This because there is a high chance that the people in this list would know each other. In the "Distant-friend", there is a less chance that one person would know each other. So it means that the person would need to travel more to find each other.
\section*{4}
The Degree distribution is $\{0, 0.2, 0.1, 0.2 , 0.2, 0.1, 0.1, 0.1\}$
\section*{5}
In this network each group is a complete graph with each other. And everyone knows the other people in the other groups.Each person has a total of 29 friends and a total of 60 enemies. This shows that the network is not stable because the enemies outnumber the total amount of friends.
\section*{6}
The nodes combination BCA and ADE satisfy the triadic closure principle
\section*{7}
To find the average path length of the network, we use this formular $\frac{\log n}{\log k}$. n is 50 and k is 10. So our calculation is $\frac{\log 50}{\log 10} = 1.7$. The closest value is B, 2.
\end{document}